
\chapter*{Publications \& Presentations}
\section*{Journal articles}
\noindent
\subsection*{2016}
%\years{2016}
\noindent1. {\underline {Zhang C.}}, Cretu O., Kvashnin D., Kawamoto N., Mitome N., Wang X., Bando Y., Sorokin P., Golberg D. "Statistically analyzed photoresponse of elastically bent CdS nanowires probed by light-compatible {\em in situ} High-Resolution TEM". {\em Nano Letters} 16(10), 6008-6013(2016); \\[5pt]
\noindent2. \underline{Zhang C.}, Wang X., Liang Q., Liu X., Weng Q., Liu J., Yang Y., Dai Z., Ding K., Bando Y. Golberg D. "Amorphous phosphorus/nitrogen-doped graphene paper for ultrastable sodium-ion batteries". {\em Nano Letters} 16(3), 2054-2060(2016);\\[5pt]
\noindent3. Xue Y., Dai P., Jiang X., Wang X., \underline{Zhang C.}, Tang D., Weng Q., Wang X., Pakdel A., Tang C. Bando Y., Golberg D. "Template-free synthesis of boron nitride foam-like porous monoliths and their high-end applications in water purification". {\em Journal of Material Chemistry A} 4(4), 1469-1478(2016);\\[5pt]
\noindent4. Hou G., Cheng B., Cao Y., Yao M., Li B., \underline{Zhang C.}, Weng Q., Wang X., Bando Y., Golberg D., Yuan F. "Scalable production of 3D plum-pudding-like Si/C spheres: Towards practical application in Li-ion batteries". {\em Nano Energy} 24, 111-120(2016); \\

\subsection*{2015}
%\years{2015}
\noindent5. \underline{Zhang C.}, Xu Z., Tian W., Wang X., Bando Y., Fukata N., Golberg D. “{\em In situ} fabrication and optoelectronic analysis of axial CdS/p-Si nanowire heterojunctions in a high-resolution transmission electron microscope”.{\em Nanotechnology} 26, 154001-8(2015);\\[5pt]
\noindent6. Xu Z., \underline{Zhang C.}, Bando Y., Bai X.D., Golberg D. “Lateral piezopotential-gated field-effect transistor of ZnO nanowires”. {\em Nano Energy} 13, 233-239(2015);\\[5pt]
\noindent7. Weng Q.H., Wang X., \underline{Zhang C.}, Jiang X., Bando Y., Golberg D. “Supercapacitive energy storage performance of molybdenum disulfide nanosheets wrapped with micoporous carbons”. {\em Journal of Material Chemistry A} 3, 3097-3102(2015); \\[5pt]
\noindent8. Wang. X, Liu D., Weng Q., Liu J., Liang X., \underline{Zhang C.} "Cu/Li4Ti5O12 scaffold as superior anode for lithium-ion batteries". {\em NPG Asia Materials} 7, 171(2015); \\[5pt]
\noindent9. \underline{Zhang C.}, Xu Z., Golberg D. " Opto-mechano-electrical tripling in ZnO nanowires probed by photocurrent spectroscopy in a high-resolution transmission electron microscope ".  {\em Applied Physics Letters} 107, 091103(2015); \\[5pt] 
\noindent10. Xue Y., Jiang B., Bourgeois B., Dai P., Mitome M., \underline{Zhang C.}, Yamaguchi M., Matveev A., Tang C., Bando Y., Tsuchiya K., Golberg D. "Aluminum matrix composites reinforced with multi-walled boron nitride nanotubes fabricated by a high-pressure torsion technique". {\em Materials \& Design} 88, 451-460(2015);\\[5pt]
\noindent11. Weng Q., Ide Y., Wang X.B., Wang X., \underline{Zhang C.}, Jiang X., Xue Y., Dai P., Komaguchi K., Bando Y., Golberg D. "Design of BN porous sheets with richly exposed (002) plane edges and their application as TiO2 visible light sensitizer". {\em Nano Energy} 16, 19-27(2015);\\[5pt]
\noindent12. Dai P., Xue Y., Wang X., Weng Q., \underline{Zhang C.}, Jiang X., Tang D., Wang X., Kawamoto N., Ide Y., Mitome M., Golberg D., Bando Y. "Pollutant capturing SERS substrate: porous boron nitride microfibers with uniform silver nanoparticle decoration". {\em Nanoscale} 7(45), 18992-18997(2015);\\

\subsection*{2014}
%\years{2014}
\noindent13. \underline{Zhang C.}, Tian W., Xu Z., Liu J., Li S., Tang D.M., Cai X., Wang X.,Weng Q., Liao M., Kawamoto N., Bando Y., Golberg D. “Photosensing performance of branched CdS/ZnO heterostructures as revealed by in situ TEM and photodetector tests”, {\em Nanoscale} 6, 8084-8090(2014);\\[5pt]
\noindent14. Golberg D., \underline{Zhang C.}, Xu Z. “Cubic lattice nanosheets: Thickness-driven light emission”, {\em ACS Nano} 8(7), 6516-6519(2014);\\[5pt]
\noindent15. Tian W., \underline{Zhang C.}, Zhai T., Li S.L., Wang X., Liu J., Jie X., Liu D., Lioa M., Koide Y., Golberg D., Bando Y. "Flexible ultraviolet photodetectors with broad photoresponse based on branched ZnS-ZnO heterostructure nanofilms”. {\em Advanced Materials} 26, 3088-3093(2014);\\[5pt]
\noindent16. Wang X., Weng Q.H., Liu X., Wang X.B., Tang D.M., Tian W., \underline{Zhang C.}, Yi W., Liu D., Bando Y., Golberg D. “Atomistic origins of high rate capability and capacity of N-doped graphene for Lithium storage”. {\em Nano Letters} 14, 1164-1171(2014);\\[5pt]
\noindent17. Wang X., Chen Z., Liu D., Tian W., Wang Q., \underline{Zhang C.}, Liu J.W., Han L., Bando Y., Golberg D. “Tripled-yolked ZnO-CdS hollow spheres for semiconductor-sensitized solar cells”, {\em Particle \& Particle Systems Characterization} 31(7), 757-762(2014);\\

\subsection*{Previously}
%\years{2012-2013}
\noindent18. Tian W., \underline{Zhang C.}, Wang X., Golberg D., Bando Y. “Flexible SnO2 hollow nanosphere film based high-performance ultraviolet photodetector”. {\em Chemical Communications} 49(36), 3739-3741(2013);\\[5pt]
\noindent19. Tian W., \underline{Zhang C.}, Wang X., Golberg D., Bando Y. "Flexible ultraviolet photodetectors with broad photoresponse based on branched ZnS-ZnO heterostructure nanofilms”. {\em Advanced Materials} 26(19), 3088–3093(2013);\\[5pt] 
\noindent20. Tian W. Wang X., Zhi C., Zhai T., Liu D., Zhang C., Golberg D., Bando Y. "Ni (OH)2 nanosheet@ Fe2O3 nanowire hybrid composite arrays for high-performance supercapacitor electrodes". {\em Nano Energy} 2(5), 754-763(2013).\\[5pt]
\noindent21. \underline{Zhang C.}, Huang H., Liang B., Wang X.F., Lan X., Xiang Q., Liu B., Chen D. "Patterned growth of In2O3 spheres organized by radially-aligned In2O3 nanobelts". {\em Journal of Nanoengineering and Nanomanufacturing} 2(2), 166-170(2012);\\[5pt]
\noindent22. Wang X.F., Huang H., Liu B., Liang B., \underline{Zhang C.}, Ji Q., Chen D., Shen G. "Shape evolution and applications in water purification: the case of CVD-grown Zn2SiO4 straw-bundles". {\em Journal of Material Chemistry} 22(12), 5330-5335(2012).\\

\section*{Oral presentations}

%\years{2016}
\noindent1. {\em Nanowire deformations and axial junction constructions in tandem with photocurrent measurements inside a transmission electron microscope}, MRS Spring 2016, Phoenix, USA(2016);\\[15pt]
%\years{2014}

\noindent2. {\em Optoelectronic properties of nanostructured materials as revealed by laser-compatible in situ Transmission Electron Microscopy}, 23rd Australian Conference on Microscopy and Microanalysis, Adelaide, Australia(2014). 

\section*{Poster presentations}
%\years{2016}
\noindent1. {\em Amorphous P@Graphene paper for ultrastable sodium-ion batteries}, AsiaNano 2016, Sapporo, Japan(2016);\\[15pt]
%\years{2015}
\noindent2. {\em In situ fabrication and photocurrent analysis of axial CdS/p-Si nanowire junctions by high-resolution TEM}, Japanese Society of Microscopy Kanto-branch meeting, Tokyo, Japan(2015). 



%\vspace{1cm}
\vfill{}
%\hrulefill