% the acknowledgments section

\newthought{I} would like to express my special appreciation to my adviser Prof. Dmitri Golberg. I thank him for encouraging my studies and for guiding me to grow as a junior researcher. His advices on research have been priceless. Prof. Golberg is always warm and encouraging. He never criticized nor complained on me, he never forced me to do anything; instead, he provided me freedom, trust and appreciations. I am very much rised by him to accomplish all research projects. \\
I would like to thank the Committee, Prof. Takayoshi Sasaki, Prof. Masahiro Sasaki, Prof. Naoki Fukata for precious wise advices. They were very kind to me but keen and strict with respect to science. \\
I am grateful to the collaborations with Prof. Naoki Fukata, Prof. Xi Wang and Prof. Wei Tian. They provided excellent samples, comprehensive performance tests and professional advices. 
Especially the credits go to Dr. Zhi Xu and Dr. Ovidiu Cretu for their instructions for microscopy and engineering, as well as writing, data processing and programming. They are incredibly smart, insightful persons with charming personalities. 
I would like to thank my {\em senppai} Dr. Qunhong Weng, not only for his experimental assistance and chemistry-related advices, but also for his scientific-wise characteristics: wisdom, diligence and integrity. \\
I thank many other colleagues and research friends in NIMS and other Institutes for every advice and assistance, namely (in family name order) Prof. Y. Bando, Prof. P. Dai, Dr. K. Hasegawa, Ms. Y. Hirai, Mr. K. Iiyama, Dr. X. Jiang, Ms. S. Kasaya, Dr. N. Kawamoto, Prof. D. Liu, Prof. X. Liu, Dr. M. Mitome, Dr. K. Moore, Mr. M. Nakatsu, Dr. A. Nukui, Dr. A. Ohi, Mr. H. Sugaya, Prof. D-M. Tang, Prof. J. Tang, Dr. Y. Xue, Dr. I. Yamada, Prof. X. Wang, Dr. M. Yamaguchi, Prof. T. Zhai, Prof. C. Zhi, Dr. M. Zhou, Mr. X. Zhou. Thank you all. 
\\
My research was conducted at the National Institute for Materials Science (NIMS), Tsukuba. I would like to acknowledge the financial support from NIMS.\\
I am grateful to University of Tsukuba, Tsukuba City and Japan, where I live and study for more than 4 years. \\
Last but not least, I would like to thank my family for their deep and endless love. I love you. \\[9ex]

\begin{flushright}
Feb 2017\\
C. Zhang\\
Tsukuba, Japan
\end{flushright}

